---
title: "Homework 3"
author: "Wenxin Tian"
date: "`r Sys.Date()`"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1:

```{r}
library(p8105.datasets)
data("instacart")
```

__Dataset description__:

The dataset shows `r nrow(instacart)` observations of `r ncol(instacart)` variables. Some key variables include product name and id, which aisle and department it was bought from, the order in which the item was added to cart, and whether the item was reordered, meaning it was ordered before by the same customer. For example, here are the first 5 products listed in the dataset:

```{r}
head(instacart, 5) |>
  knitr::kable()
```

__Questions:__

__1. How many aisles are there, and which aisles are the most items ordered from?__

```{r}
instacart |>
  group_by(aisle) |>
  summarize(count = n()) |>
  arrange(desc(count))
```

There are 134 aisles, and the top 5 aisles where the most items are ordered from are fresh vegetables, fresh fruits, packaged vegetable and fruits, yogurt, and packaged cheese.

__2. Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.__

```{r}
instacart |>
  group_by(aisle) |>
  summarize(count = n()) |>
  filter(count >= 10000) |>
  arrange(desc(count)) |>
  mutate(aisle = fct_reorder(aisle, count)) |> # had to reorder the aisle factor
  ggplot(
    aes(x = count, y = aisle),
  ) +
  geom_col() +
  labs(
      title = "Popular Aisles",
      x = "Item Count",
      y = "Aisle"
    ) +
  theme_minimal()
```

__3. Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.__

```{r}
baking = 
  instacart |>
  filter(aisle == "baking ingredients") |>
  group_by(product_name) |>
  summarize(count = n()) |>
  arrange(desc(count)) |>
  head(3) |>
  mutate(aisle = "Baking Ingredients") |>
  relocate(aisle)

dog_food =
  instacart |>
  filter(aisle == "dog food care") |>
  group_by(product_name) |>
  summarize(count = n()) |>
  arrange(desc(count)) |>
  head(3) |>
  mutate(aisle = "Dog Care and Food") |>
  relocate(aisle)

veg_fruit = 
  instacart |>
  filter(aisle == "packaged vegetables fruits") |>
  group_by(product_name) |>
  summarize(count = n()) |>
  arrange(desc(count)) |>
  head(3) |>
  mutate(aisle = "Packaged Vegetable and Fruits") |>
  relocate(aisle)

knitr::kable(
  list(baking, dog_food, veg_fruit),
  caption = "Most Popular Items in Following Aisles"
)

# Simpler way:

instacart |>
  group_by(aisle, product_name) |>
  filter(
    aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")
    ) |>
  summarize(count = n()) |> 
  arrange(desc(count)) |>
  slice(1:3) |>
  knitr::kable(caption = "Most Popular Items in Following Aisles")
```

__4. Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).__

```{r}
instacart |>
  group_by(product_name, order_dow) |>
  summarize(mean_hour = mean(order_hour_of_day)) |>
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) |>
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) |>
  rename(
    "Sunday" = "0",
    "Monday" = "1",
    "Tuesday" = "2",
    "Wednesday" = "3",
    "Thursday" = "4",
    "Friday" = "5",
    "Saturaday" = "6"
  ) |>
  knitr::kable(
    caption = "Mean Hour of Day at Which Following Products are Ordered:"
  )
```

## Problem 2:

```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

__1. Data Cleaning:__

- format the data to use appropriate variable names;
- focus on the “Overall Health” topic
- include only responses from “Excellent” to “Poor”
- organize responses as a factor taking levels ordered from “Poor” to “Excellent”

```{r}
brf = 
  brfss_smart2010 |>
  janitor::clean_names() |>
  rename(
    "state" = locationabbr,
    "location" = locationdesc) |>
  filter(
    topic == "Overall Health",
    response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")
  )

response = ordered(pull(brf, response), levels = c("Poor", "Fair", "Good", "Very good", "Excellent"))
```

__2. In 2002, which states were observed at 7 or more locations? What about in 2010?__

```{r}
states_2002 =
  brf |>
  group_by(year, state, location) |>
  summarize() |>
  count(state) |>
  filter(
    year == 2002,
    n >= 7
  ) |>
  pull(state)

states_2010 =
  brf |>
  group_by(year, state, location) |>
  summarize() |>
  count(state) |>
  filter(
    year == 2010,
    n >= 7
  ) |>
  pull(state)
```

In 2002, the states that were observed in more than 7 places are `r states_2002`. In 2010, the list changed to `r states_2010`.